---
title: "HongxiaoYU_Assignment#8"
output: html_notebook
author: "Hongxiao_YU"
date: "April_4_2020"
---

 


*** question 1
# note:
# a = a data frame with the individual item responses
# (individuals in rows and items in columns)
# b = a numeric with the scale used for the items
# c = a numeric vector indicating which item numbers should be #reverse scored
```{r}
datareverse <- function (a,b,c) {
  # add an attitional column
 a$rev.score <- c((b + 1) - a[,c])
 print(a)
}

```
***



*** question 2
# create a CSV file
```{r}
row1 <- c(2, 3, 4, 6, 3, 3, 4, 1)
row2 <- c(2, 3, 4, 6, 3, 5, 1, 6)
row3 <- c(2, 4, 6, 1, 5, 2, 3, 5)
row4 <- c(3, 2, 4, 5, 2, 4, 5, 4)
row5 <- c(2, 1, 4, 2, 5, 6, 3, 2)
data <- rbind(row1, row2, row3, row4, row5)
write.csv(data, 'hongxiao_csv')
data
```

# send it to my function for scoring
```{r}
library(here)
csv.file <- read.csv(here("data", "hongxiao_csv"),header = TRUE)
data.1 <- datareverse(csv.file[,2:9], 6, 1)
data.2 <- datareverse(csv.file[,2:9], 6, 2)
data.3 <- datareverse(csv.file[,2:9], 6, 3)
data.final <- cbind(data.1, data.2[,9], data.3[,9])
data.final
write.csv(data.final, 'hongxiao_final_csv')
```



***
Question 3
```{r}
library(here)
hsb2 <- read.csv(here("data", "hsb2.csv"))
hsb2$gender <- factor(hsb2$female, levels = c(0,1),
                    labels = c("male", "female"))
ggplot(data = hsb2) +
  geom_point(mapping = aes(x = math, y = science, color = gender))
```
***


***
# Question 4
```{r}
ggplot(data = hsb2) +
  geom_point(mapping = aes(x = math, y = science)) +
  facet_wrap(~ gender)
```
***



***
#Question 5
### try out geam_vlolin, it is a very interesting graph.
```{r}
ggplot(data = hsb2) +
  geom_violin(mapping = aes(x = math, y = science)) +
  facet_wrap(~ gender)
```

***


